Through the eyes of the teacher

### 2022-02-17 01_studies/01_Laborstudie ProVisioNET/R script/demographic data/demographic data script.Rmd
update r script

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf #bookdown::word_document2
---

@@

# format and insert table in manuscript
apa_table(
  demo.table,
  caption = "Demographic Information and and Teaching Experience",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )

>>>>

documentclass     : "apa6"
classoption       : "man"
output            : bookdown::word_document2
---

@@

# format and insert table in manuscript
apa_table(
  demo.table,
  caption = "Demographic Information and Teaching Experience",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )
